---
title: "midterm"
author: "Karl Rohe"
output: md_document
---
  
## Midterm.
#install.packages("maps")
#### 1.  Map the delay by destination.
  
  Compute the average delay by destination, then join on the airports data frame so you can show the spatial distribution of delays. Here’s an easy way to draw a map of the United States.  You are welcome to use this code or some other code. 

```{r} 
#flights
#planes
#airlines
#airports
#weather
library(tidyverse)
library(nycflights13)
flights = nycflights13::flights


flights2 = flights %>% group_by(dest) %>%
  summarize(avgDelay = mean(dep_delay, na.rm = TRUE)) 

airports %>%
  right_join(flights2,c("faa" = "dest")) %>%
  ggplot(aes(lon, lat)) +
  borders("state")+ 
  geom_point(aes(colour = avgDelay)) +
  scale_size_area()+
  coord_quickmap()
```

#### 2.   Do planes trade ownership?

You might expect that there’s an implicit relationship between plane and airline, because each plane is flown by a single airline. Confirm or reject this conjecture using data.

This analysis shows that there are duplicated tailnums used by each unique airline/tailnum pair. Therefore each plane is not flown by a single airline so I reject this conjecture
```{r}
planes_unique = planes %>% left_join(flights, "tailnum")
planes2 = planes_unique %>% select(carrier, tailnum) %>%
  distinct()
planes2

planes2$tailnum[duplicated(planes2$tailnum)]



```


#### 3.  Plane's average speed.

Notice that ```flights$air_time``` is in minutes.  Make a new column that is the air time in hours. 

```{r}
flights_1 = flights %>% mutate(air_timeHours = (air_time / 60))
flights_1
```


#### 4. Average speed

For each flight, compute the average speed of that flight (in miles per hour).  Then, for each plane, compute the average of those average speeds. Display it in a histogram. You can use a base R histogram ```hist``` or ggplot's ```geom_histogram```. 

```{r}
flights_1 %>% mutate(avgSpeed = distance/air_timeHours)%>%
  group_by(tailnum)%>%
  summarize(avgAllPlanes = mean(avgSpeed, na.rm=TRUE)) %>%
  ggplot(aes(avgAllPlanes))+
  geom_histogram()
```




#### 5. What correlates with average speed?

To examine if there is anything in the plane data that correlates with average speed, use ```geom_boxplot``` with average speed of the plane (in previous question) on the y-axis and ```planes$engine``` on the x-axis.  Do the same for ```planes$engines``` and ```planes$type```.  

```{r}
# put answer here
```

PLEASE REMEMBER TO ALSO COMMIT AND PUSH YOUR FIGURES!!!
