---
title: "midterm"
author: "Karl Rohe"
output: md_document
---
  
## Midterm.
  
#### 1.  Map the delay by destination.
  
  Compute the average delay by destination, then join on the airports data frame so you can show the spatial distribution of delays. Here’s an easy way to draw a map of the United States.  You are welcome to use this code or some other code. 

```{r} 
library(tidyverse)
library(nycflights13)

airports %>%
  semi_join(flights, c("faa" = "dest")) %>%
  ggplot(aes(lon, lat)) +
  borders("state") +
  geom_point() +
  coord_quickmap()
```

You might want to use the size or colour of the points to display the average delay for each airport.

```{r}

flights
planes
airlines
airports
weather

# put your answer here.
```


#### 2.   Do planes trade ownership?

You might expect that there’s an implicit relationship between plane and airline, because each plane is flown by a single airline. Confirm or reject this conjecture using data.

```{r}
# put your answer here. 
```


#### 3.  Plane's average speed.

Notice that ```flights$air_time``` is in minutes.  Make a new column that is the air time in hours. 

```{r}
# put your answer here.  
```


#### 4. Average speed

For each flight, compute the average speed of that flight (in miles per hour).  Then, for each plane, compute the average of those average speeds. Display it in a histogram. You can use a base R histogram ```hist``` or ggplot's ```geom_histogram```. 

```{r}
# put your answer here.  
```




#### 5. What correlates with average speed?

To examine if there is anything in the plane data that correlates with average speed, use ```geom_boxplot``` with average speed of the plane (in previous question) on the y-axis and ```planes$engine``` on the x-axis.  Do the same for ```planes$engines``` and ```planes$type```.  

```{r}
# put answer here
```

PLEASE REMEMBER TO ALSO COMMIT AND PUSH YOUR FIGURES!!!
